### 2025-02-23 paper/sections/Abstract.tex
add abstract

\begin{abstract}
    salam.
    khobi.
\end{abstract}

>>>>

\begin{abstract}
This paper presents a comprehensive study on multilingual emotion classification, aimed at advancing the detection and analysis of emotions in textual data across diverse languages. The research is structured into three distinct tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection. To address challenges associated with linguistic variability and limited annotated data, we employ a combination of deep learning techniques, including Long Short-Term Memory networks, transformer-based embeddings fine-tuned via low-rank adaptation, and classifiers such as SVMs\footnote{Support Vector Machines} and XGBoost. Extensive experiments conducted on datasets covering both high and low resource languages demonstrate that innovative preprocessing and domain adaptation strategies significantly enhance model performance, as evidenced by competitive macro-average F1 scores. Despite these promising results, the study acknowledges limitations arising from the scarcity of annotated data in underrepresented languages and the inherent complexity of capturing nuanced emotional expressions. The findings underscore the importance of developing robust, language-aware emotion recognition systems and suggest that future research should focus on expanding multilingual datasets, refining model architectures, and exploring zero-shot learning techniques.
\end{abstract}

### 2025-02-23 paper/sections/Conclusion.tex
add abstract

\section{Conclusion}
This study investigated multilingual emotion classification, addressing the challenges of detecting and analyzing emotions across diverse linguistic contexts. By structuring the problem into three tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection—we evaluated multiple machine learning and deep learning approaches to improve emotion recognition across various languages. Our findings demonstrate the effectiveness of leveraging language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in enhancing model performance.

The significance of this research lies in its contribution to multilingual emotion recognition, particularly for low-resource languages. Our methodology, integrating deep learning models such as LSTMs, transformer-based embeddings, and classification techniques like SVM and XGBoost, achieved competitive results in emotion classification tasks. The study underscores the importance of language-aware preprocessing and domain adaptation techniques in addressing linguistic diversity.

>>>>

\section{Conclusion}
This study investigated multilingual emotion classification, addressing the challenges of detecting and analyzing emotions across diverse linguistic contexts. By structuring the problem into three tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection—we evaluated multiple machine learning and deep learning approaches to improve emotion recognition across various languages. Our findings demonstrate the effectiveness of leveraging innovative preprocessing techniques, domain adaptation strategies, and transfer learning in enhancing model performance.

The significance of this research lies in its contribution to multilingual emotion recognition, particularly for low-resource languages. Our methodology, integrating deep learning models such as LSTMs, transformer-based embeddings, and classification techniques like SVM and XGBoost, achieved competitive results in emotion classification tasks. The study underscores the importance of innovative preprocessing and domain adaptation techniques in addressing linguistic diversity.

### 2025-02-23 paper/sections/ExperimentalSetup.tex
add abstract

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
\input{tables/MainResults}

>>>>

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
% \input{tables/MainResults}
\begin{table*}[h]
    \centering
    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model(Baseline)\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
    \label{tab:results}
    \resizebox{2\columnwidth}{!}{
        \begin{tabular}{l|c|ccc|cccc|cccc}
            \hline
                                                    &                                                                                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                         \\
            \cline{3-13}
            \textbf{Language}                       & \textbf{Our Model}                                                                           & \textbf{Ours}                & \textbf{Best}                & \textbf{Rank}               & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} \\
            \hline
            Afrikaans(afr)                          & \citep{wang2024multilingual} + SVM                                                           & 54.01                        & 69.86                        & 15/37                       & —             & —             & —                 & —             & 54.01         & 70.50         & 61.28             & 4/14          \\
            Amharic(amh)                            & \citep{arabert}               + SVM                                                          & 61.20                        & 77.31                        & 19/43                       & 49.42         & 85.58         & —                 & 14/23         & 61.20         & 66.68         & —                 & 6/13          \\
            Algerian Arabic(arq)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.07                        & 66.87                        & 24/43                       & 36.54         & 63.38         & 36.37             & 18/26         & 51.07         & 65.35         & 55.75             & 6/14          \\
            Moroccan Arabic(ary)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.88                        & 62.92                        & 20/41                       & —             & —             & —                 & —             & 51.88         & 63.22         & 52.76             & 6/12          \\
            Chinese(chn)                            & ZPoint Large\footnote{\url{https://huggingface.co/iampanda/zpoint_large_embedding_zh}} + SVM & 56.65                        & 70.94                        & 30/41                       & 48.47         & 72.24         & 51.86             & 19/27         & 56.65         & 56.65         & 55.23             & 7/15          \\
            German(deu)                             & \citep{wang2024multilingual}       + SVM                                                     & 60.60                        & 73.99                        & 25/50                       & 54.10         & 76.57         & 56.21             & 18/27         & 60.60         & 73.62         & 59.17             & 6/15          \\
            English(eng)                            & \citep{zhang2025jasperstelladistillationsota}                                                & 73.97                        & 82.30                        & 35/96                       & 68.81         & 84.04         & 64.15             & 28/43         & 73.97         & 82.07         & 65.58             & 4/17          \\
            Spanish(esp)                            & \citep{wang2024multilingual}      + SVM                                                      & 76.19                        & 84.88                        & 26/47                       & 66.70         & 80.80         & 72.59             & 23/29         & 76.19         & 85.00         & 73.29             & 5/15          \\
            Hausa(hau)                              & \citep{dobler-demelo-2023-focus} + SVM                                                       & 63.22                        & 75.07                        & 18/40                       & 58.42         & 77.00         & 39.16             & 15/26         & 63.22         & 73.14         & 51.91             & 4/13          \\
            Hindi(hin)                              & \citep{wang2024multilingual}  + SVM                                                          & 80.32                        & 92.57                        & 33/43                       & —             & —             & —                 & —             & 80.32         & 92.16         & 79.73             & 6/16          \\
            Igbo(ibo)                               & \citep{wang2024multilingual}   + SVM                                                         & 50.93                        & 60.01                        & 14/34                       & —             & —             & —                 & —             & 50.93         & 60.47         & 37.40             & 4/12          \\
            Indonesian(ind)                         & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 35.64         & 67.24         & 57.29             & 15/17         \\
            Javanese(jav)                           & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 25.62         & 25.62         & 50.47             & 12/13         \\
            Kinyarwanda(kin)                        & \citep{wang2024multilingual}  + SVM                                                          & 51.94                        & 65.74                        & 6/31                        & —             & —             & —                 & —             & 51.94         & 64.59         & 34.36             & 2/11          \\
            Marathi(mar)                            & \citep{wang2024multilingual}   + SVM                                                         & 81.10                        & 90.58                        & 23/42                       & —             & —             & —                 & —             & 81.10         & 90.42         & 77.24             & 6/13          \\
            Oromo(orm)                              & \citep{wang2024multilingual}    + SVM                                                        & 54.31                        & 61.64                        & 11/36                       & —             & —             & —                 & —             & 54.31         & 60.07         & —                 & 3/11          \\
            Nigerian-Pidgin(pcm)                    & \citep{wang2024multilingual}   + SVM                                                         & 53.09                        & 67.40                        & 22/34                       & —             & —             & —                 & —             & 53.09         & 67.40         & 48.67             & 5/10          \\
            Pt\footnote{Portuguese} Brazilian(ptbr) & \citep{souza2020bertimbau} + SVM                                                             & 47.99                        & 68.33                        & 27/42                       & 38.20         & 71.00         & 46.72             & 22/25         & 47.99         & 68.36         & 51.60             & 8/14          \\
            Pt Mozambican(ptmz)                     & \citep{wang2024multilingual}   + SVM                                                         & 50.08                        & 54.77                        & 6/36                        & —             & —             & —                 & —             & 50.08         & 55.54         & 40.44             & 3/14          \\
            Romanian(ron)                           & \citep{wang2024multilingual}     + SVM                                                       & 73.75                        & 79.43                        & 14/43                       & 57.61         & 72.60         & 57.69             & 19/26         & 73.75         & 77.27         & 76.23             & 4/15          \\
            Russian(rus)                            & \citep{snegirev2025russianfocusedembeddersexplorationrumteb}     + SVM                       & 82.42                        & 90.87                        & 33/50                       & 78.41         & 92.54         & 87.66             & 22/30         & 82.42         & 90.62         & 76.97             & 6/17          \\
            Somali(som)                             & \citep{wang2024multilingual}       + SVM                                                     & 48.26                        & 57.65                        & 10/34                       & —             & —             & —                 & —             & 48.26         & 56.66         & —                 & 4/13          \\
            Sundanese(sun)                          & \citep{wang2024multilingual}      + SVM                                                      & 42.48                        & 54.97                        & 19/37                       & —             & —             & —                 & —             & 42.48         & 50.72         & 46.33             & 4/11          \\
            Swahili(swa)                            & \citep{wang2024multilingual}      + SVM                                                      & 29.52                        & 41.47                        & 15/32                       & —             & —             & —                 & —             & 29.52         & 38.43         & 33.27             & 5/14          \\
            Swedish(swe)                            & \citep{wang2024multilingual}     + SVM                                                       & 56.51                        & 62.62                        & 13/40                       & —             & —             & —                 & —             & 56.51         & 64.53         & 51.18             & 6/13          \\
            Tatar(tat)                              & \citep{wang2024multilingual}    + SVM                                                        & 64.32                        & 84.59                        & 18/36                       & —             & —             & —                 & —             & 64.32         & 83.59         & 60.66             & 5/11          \\
            Tigrinya(tir)                           & \citep{wang2024multilingual}    + SVM                                                        & 52.37                        & 59.05                        & 6/34                        & —             & —             & —                 & —             & 52.37         & 55.24         & —                 & 2/10          \\
            Ukrainian(ukr)                          & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 48.62                        & 72.56                        & 29/40                       & 42.55         & 70.75         & 43.54             & 17/24         & 48.62         & 71.99         & 54.76             & 10/17         \\
            Emakhuwa(vmw)                           & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 16.81                        & 32.50                        & 5/31                        & —             & —             & —                 & —             & 16.80         & 26.02         & 20.41             & 6/9           \\
            isiXhosa(xho)                           & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.64         & 44.26         & 30.79             & 6/10          \\
            Yoruba(yor)                             & \citep{wang2024multilingual}     + SVM                                                       & 34.09                        & 46.13                        & 9/32                        & —             & —             & —                 & —             & 34.09         & 46.79         & 27.44             & 4/11          \\
            isiZulu(zul)                            & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.35         & 16.35         & 22.03             & 8/11          \\
            \hline
        \end{tabular}
    }
\end{table*}

### 2025-02-23 paper/sections/SystemOverview.tex
add abstract

Following feature extraction, we applied multiple classification algorithms to perform the multi-label classification task. One of the classifiers used was the Multi-Layer Perceptron (MLP), a feedforward artificial neural network capable of modeling complex relationships between the extracted features and the target labels. Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}. Furthermore, SVMs\footnote{Support Vector Machines} were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.

>>>>

Following feature extraction, we applied multiple classification algorithms to perform the multi-label classification task. One of the classifiers used was the Multi-Layer Perceptron (MLP), a feedforward artificial neural network capable of modeling complex relationships between the extracted features and the target labels. Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}. Furthermore, SVMs were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.

### 2025-02-23 paper/sections/introduction.tex
add abstract

To address these limitations, we present a comprehensive analysis of state-of-the-art methodologies and evaluate their effectiveness across multiple languages. Our findings highlight the critical role of language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in improving multilingual emotion classification.

>>>>

To address these limitations, we present a comprehensive analysis of state-of-the-art methodologies and evaluate their effectiveness across multiple languages. Our findings highlight the critical role of innovative preprocessing techniques, domain adaptation strategies, and transfer learning in improving multilingual emotion classification.

### 2025-02-23 paper/tables/MainResults.tex
add abstract

\begin{table*}[h]
    \centering
    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
    \label{tab:results}
    \resizebox{2\columnwidth}{!}{
        \begin{tabular}{l|ccc|cccc|cccc}
            \hline
                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                                     \\
            \cline{2-12}
            \textbf{Language} & \textbf{Our Model}               & \textbf{Best Model}          & \textbf{Rank}               & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} \\
            \hline
            afr               & 54.01                        & 69.86                        & 15/37                       & —              & —                   & —                & —             & 54.01          & 70.50               & 61.28            & 4/14          \\
            amh               & 61.20                        & 77.31                        & 19/43                       & 49.42          & 85.58               & —                & 14/23         & 61.20          & 66.68               & —                & 6/13          \\
            arq               & 51.07                        & 66.87                        & 24/43                       & 36.54          & 63.38               & 36.37            & 18/26         & 51.07          & 65.35               & 55.75            & 6/14          \\
            ary               & 51.88                        & 62.92                        & 20/41                       & —              & —                   & —                & —             & 51.88          & 63.22               & 52.76            & 6/12          \\
            chn               & 56.65                        & 70.94                        & 30/41                       & 48.47          & 72.24               & 51.86            & 19/27         & 56.65          & 56.65               & 55.23            & 7/15          \\
            deu               & 60.60                        & 73.99                        & 25/50                       & 54.10          & 76.57               & 56.21            & 18/27         & 60.60          & 73.62               & 59.17            & 6/15          \\
            eng               & 73.97                        & 82.30                        & 35/96                       & 68.81          & 84.04               & 64.15            & 28/43         & 73.97          & 82.07               & 65.58            & 4/17          \\
            esp               & 76.19                        & 84.88                        & 26/47                       & 66.70          & 80.80               & 72.59            & 23/29         & 76.19          & 85.00               & 73.29            & 5/15          \\
            hau               & 63.22                        & 75.07                        & 18/40                       & 58.42          & 77.00               & 39.16            & 15/26         & 63.22          & 73.14               & 51.91            & 4/13          \\
            hin               & 80.32                        & 92.57                        & 33/43                       & —              & —                   & —                & —             & 80.32          & 92.16               & 79.73            & 6/16          \\
            ibo               & 50.93                        & 60.01                        & 14/34                       & —              & —                   & —                & —             & 50.93          & 60.47               & 37.40            & 4/12          \\
            ind               & —                            & —                            & —                           & —              & —                   & —                & —             & 35.64          & 67.24               & 57.29            & 15/17         \\
            jav               & —                            & —                            & —                           & —              & —                   & —                & —             & 25.62          & 25.62               & 50.47            & 12/13         \\
            kin               & 51.94                        & 65.74                        & 6/31                        & —              & —                   & —                & —             & 51.94          & 64.59               & 34.36            & 2/11          \\
            mar               & 81.10                        & 90.58                        & 23/42                       & —              & —                   & —                & —             & 81.10          & 90.42               & 77.24            & 6/13          \\
            orm               & 54.31                        & 61.64                        & 11/36                       & —              & —                   & —                & —             & 54.31          & 60.07               & —                & 3/11          \\
            pcm               & 53.09                        & 67.40                        & 22/34                       & —              & —                   & —                & —             & 53.09          & 67.40               & 48.67            & 5/10          \\
            ptbr              & 47.99                        & 68.33                        & 27/42                       & 38.20          & 71.00               & 46.72            & 22/25         & 47.99          & 68.36               & 51.60            & 8/14          \\
            ptmz              & 50.08                        & 54.77                        & 6/36                        & —              & —                   & —                & —             & 50.08          & 55.54               & 40.44            & 3/14          \\
            ron               & 73.75                        & 79.43                        & 14/43                       & 57.61          & 72.60               & 57.69            & 19/26         & 73.75          & 77.27               & 76.23            & 4/15          \\
            rus               & 82.42                        & 90.87                        & 33/50                       & 78.41          & 92.54               & 87.66            & 22/30         & 82.42          & 90.62               & 76.97            & 6/17          \\
            som               & 48.26                        & 57.65                        & 10/34                       & —              & —                   & —                & —             & 48.26          & 56.66               & —                & 4/13          \\
            sun               & 42.48                        & 54.97                        & 19/37                       & —              & —                   & —                & —             & 42.48          & 50.72               & 46.33            & 4/11          \\
            swa               & 29.52                        & 41.47                        & 15/32                       & —              & —                   & —                & —             & 29.52          & 38.43               & 33.27            & 5/14          \\
            swe               & 56.51                        & 62.62                        & 13/40                       & —              & —                   & —                & —             & 56.51          & 64.53               & 51.18            & 6/13          \\
            tat               & 64.32                        & 84.59                        & 18/36                       & —              & —                   & —                & —             & 64.32          & 83.59               & 60.66            & 5/11          \\
            tir               & 52.37                        & 59.05                        & 6/34                        & —              & —                   & —                & —             & 52.37          & 55.24               & —                & 2/10          \\
            ukr               & 48.62                        & 72.56                        & 29/40                       & 42.55          & 70.75               & 43.54            & 17/24         & 48.62          & 71.99               & 54.76            & 10/17         \\
            vmw               & 16.81                        & 32.50                        & 5/31                        & —              & —                   & —                & —             & 16.80          & 26.02               & 20.41            & 6/9           \\
            xho               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.64          & 44.26               & 30.79            & 6/10          \\
            yor               & 34.09                        & 46.13                        & 9/32                        & —              & —                   & —                & —             & 34.09          & 46.79               & 27.44            & 4/11          \\
            zul               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.35          & 16.35               & 22.03            & 8/11          \\
            \hline
        \end{tabular}
    }
\end{table*}

>>>>

% Multilingual-E5-large-instruct \citep{wang2024multilingual}
% AraBert Large Algerian \citep{arabert}
